---
title: "azure"
output: html_document
date: "2024-05-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(DBI)
library(odbc)
library(tidyverse)
```

```{r}
 con <- dbConnect(odbc::odbc(),
                 Driver = "ODBC Driver 18 for SQL Server",
                 Server = "evoo.database.windows.net",
                 Database = "chanks",
                 Uid = "cwh",
                 Pwd = "Movienight29",
                 Port = 1433,
                 Encrypt = "yes",
                 TrustServerCertificate = "no",
                 ConnectionTimeout = 30)
```

The old way: 
```{r}
store_query = "SELECT * from grocery.store"
store = dbGetQuery(con, store_query)

trip_query = "SELECT * from grocery.trips"
trip = dbGetQuery(con, trip_query)

item_query = "SELECT * from grocery.items"
item = dbGetQuery(con, item_query)

```

The chunk above is repitive and inefficient. Let's do this better: 
```{r}
tables = c('store','trips','items')

```

Ok let's write a script that creates the a list of the 3 queries we need to grab the 3 tables: 

```{r}
query_list = list() 
```


```{r}
#remember how do to do a for loop in R....? 
for (i in 1:3)
{
  query_list[i] <- paste("SELECT * from grocery.", tables[i],sep = '')
}
```

Or using lapply() 
```{r}
query_list = lapply(tables, function(x) paste0("SELECT * from grocery.",x))
```


```{r}
query_list
```

before formalizing this process into one function, let's try to execute a query from this list: 
```{r}
test_query = dbGetQuery(con, query_list[[1]])
```

```{r}

queries = list() 

for (i in 1:length(tables)){
  queries[[i]] = dbGetQuery(con, query_list[[i]])
}
```


```{r}
queries[[3]]
```



ok... now to query the db with the 3 queries we have generated: 

```{r}
# input: a list of table names
# output: a list of dataframes

querier = function(tables) 
{ 
  query_list = lapply(tables, function(x) paste0("SELECT * from grocery.",x))
  df_list = list()
  
  for (i in 1:length(tables))
  {
    df_list[[i]] = dbGetQuery(con, query_list[[i]])
  }
  return(df_list)
}
```

let's try it out: 
```{r}
querier(tables)
```


```{r}
dfs = querier(tables)
```

```{r}
stores = dfs[1]
trips = dfs[2]
items = dfs[3]
```

```{r}
items
```
###########

We now have our data, let's create visualization in ggplot as proof of concept: 

```{r}
trips = trips[[1]]
```


How many trips per store ? 
```{r}
trips_with_store_name = inner_join(trips, store, by = c("store_id" = "id"))
```

```{r}
trips_with_store_name %>% group_by(name) %>% count() %>%
  ggplot(aes(x = n, y = reorder(name, n))) + geom_col(aes(fill = name)) +
  labs(title = "Store Shoppping Frequency (Sep 2023 - May 2024)", x = "Number of Visits", y = "Store")
```

